Methods

### 2021-08-30 Manuscript/Manuscript_Methods.Rmd
methods update

We built an R [@rstat] based framework with the aim of simplifying two aspects of systematic reviews: record acquisition and relevance classification. The framework is composed by several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected. Check Supplemental Material S1 for an in-depth description of the framework and how to use it.\
The tasks carried out by the framework are grouped into "sessions", that is a set of actions that starts from a search query with which collect a set of unlabelled records and ends with the having a fully labelelled set (Fig. 1). From this labelled set, the framework allows to generate a new query and perform a new session.\
Follows a description of the method components.

![Metods' visual depiction](methods_diagram.png)
### Records' acquisition
We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE, Web Of Science (WOS) and the Institute of Electrical and Electronics Engineers (IEEE). The user needs to input a boolean query and a date range. For WOS an API key is nece

>>>>

We built an R [@rstat] based framework with the aim of simplifying two aspects of systematic reviews: record acquisition and relevance classification. The framework is composed by several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected. Check Supplemental Material S1 for an in-depth description of the framework and how to use it.\
The tasks carried out by the framework are grouped into "sessions", that is a set of actions that starts from a search query with which collect a set of unlabelled records and ends with the having a fully labelelled set (Fig. 1). From this labelled set, the framework allows to generate a new query and perform a new session.\
It is advisable that the research starts using the framework with a specific query from which she expects a high relevant/non-relevant record ratio.\
Follows a description of the framework's components.\

![Figure 1. Framework visual depiction.](methods_diagram.png)
### Records' acquisition
We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE (https://pubmed.ncbi.nlm.nih.gov/), Web Of Science (WOS, https://apps.webofknowledge.com/) and the Institute of Electrical and Electronics Engineers (IEEE, https://ieeexplore.ieee.org/Xplore/home.jsp). The user needs to input a search query and a date range. The query may contain boolean operators AND, OR, NOT and nested parentheses. The dabatase will be also called "sources" in the rest of the text.\
For WOS an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, webscraping-based solution will be employed; for MEDLINE the API key is required for high frequency requests to the NCBI server [@pubmed], which may happen if the chosen query produces a large number of records, since our tool splits a big API requests in multiple smaller ones.\
It is also possible to download and import records in the framework manually. This is particularly useful to acquire records from the SCOPUS (https://www.scopus.com/search/form.uri?display=basic#basic) and EMBASE databases (https://www.embase.com/#advancedSearch/default), for which a comprehensive API interface was not easy to build; the framework will be able to import the manually downloaded results seamlessly.A short guide on how to setup the search for each supported database is available in Supplemental Material S3.\
Once the records are dowloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, and ordering the records by simple query term frequency, putting the most likely relevant on top. The output is an "Annotation file".

### Document-Term matrix generation
